Reproducible research in archaeology using R & rrtools

### 2018-03-06 analysis/paper/paper.Rmd
up to slide 9

## Narrative to accompany the slides

- Slide 1: Title slide

@@

- Slide 2: Motivation

@@

- Slide 3: Outline

@@

- Slide 4: Current uses of R [signpost slide only]

- Slide 5: Articles in all sciences citing R

@@

- Slide 6: Archaeology articles citing R

@@

- Slide 7: What are archaeologists doing with R?

@@

>>>>

# Narrative to accompany the slides

## Slide 1: Title slide

@@

## Slide 2: Motivation

@@

## Slide 3: Outline

@@

##- Slide 4: Current uses of R [signpost slide only]

## Slide 5: Articles in all sciences citing R

@@

## Slide 6: Archaeology articles citing R

@@

## Slide 7: What are archaeologists doing with R?

@@

This plot supports our initial observations from the journals titles, which is that archaeologists using R tend to be doing more scientific archaeology. We see that many words relating to stone artefacts, zooarchaeology, and geoarchaeology are more frequently used by R-using archaeologists. On the other hand, articles that do not cite R more often discuss the Neolithic and metal-age periods, and less often reflect a technical specialisation.

## Slide 8: The unrealised potential of R for reproducible research [signpost slide only]

## Slide 9: The unrealised potential of R for reproducible research [signpost slide only]

We would now like to focus on a small sub-set of these papers using R, because they are doing something very interesting that we think all archaeologists using a programming language should be doing. This subset of papers are demonstrating the potential of R for open and reproducible research.
